Methods

### 2023-09-09 notebook/methods.qmd
Use a chunk name

```{r}
#| column: screen-inset
preds_all %>% 
  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup() %>% 
  gt() %>% 
  cols_align(align = "left") %>% 
  cols_label(
    feat_org = "Organization",
    feat_issue = "Issue",
    feat_transp = "Transparency",
    feat_acc = "Accountability",
    feat_funding = "Funding",
    feat_govt = "Relationship",
    avg = "Median probability"
  ) %>% 
  opts_theme() %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, use_filters = TRUE)
```

>>>>

```{r show-full-grid-preds}
#| column: screen-inset
preds_all %>% 
  group_by(feat_org, feat_issue, feat_transp, feat_acc, feat_funding, feat_govt) %>% 
  summarize(avg = mean(.epred)) %>% 
  ungroup() %>% 
  gt() %>% 
  cols_align(align = "left") %>% 
  cols_label(
    feat_org = "Organization",
    feat_issue = "Issue",
    feat_transp = "Transparency",
    feat_acc = "Accountability",
    feat_funding = "Funding",
    feat_govt = "Relationship",
    avg = "Median probability"
  ) %>% 
  opts_theme() %>% 
  opt_interactive(use_compact_mode = TRUE, use_highlight = TRUE, use_filters = TRUE)
```
